Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-09 paper.tex
Add C_P convergence plot

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions, to allow the revolution-averaged performance coefficient
to converge to within $\sim 1$ percentage point. Computations for the 3-D cases
were run on 192 processes (24 nodes $\times$ 8 cores each on Sandia National
Labs' Red Mesa high performance computing cluster) and took on the order of
1,000 CPU hours per second of simulated time. The 2-D simulations were run on a
single processor and took on the order of one CPU hour per simulated second.

>>>>

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions, to allow the revolution-averaged performance coefficient
to converge to within $\sim 1$ percentage point; cf.
Figure~\ref{fig:cp-convergence}. Computations for the 3-D cases were run on 192
processes (24 nodes $\times$ 8 cores each on Sandia National Labs' Red Mesa high
performance computing cluster) and took on the order of 1,000 CPU hours per
second of simulated time. The 2-D simulations were run on a single processor and
took on the order of one CPU hour per simulated second.

    \includegraphics[width=0.75\textwidth]{cp-time-series}

    \caption{Revolution-averaged power coefficient versus rotor revolution
    simulated with the 3-D $k$--$\omega$ SST model.}

    \label{fig:cp-convergence}
\end{figure}
